---
title: "SRT411 Assignment 0"
author: "Rashmi Chauhan"
date: "March 1, 2019"
output:
  pdf_document: default
html_document:
  df_print: paged
Username(GitHub): rchauhan11
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Introduction to Assignment###
For this particular assignment, I am going to perform To-do list as provided in the link [^1]. With that, I need to convert the file with .rmd extenstion to .pdf extension using knitr. In addition, its also helpful in learning content like [^2],[^3],[^4],[^5],[^6],[^7] from the website. And finally, I will learn how to make repositiories to present my files on github using my account credentials.


The TO-DO 

1)
```{r}
((2018-2014)/(2014-1999))*100
```

2)
```{r}
a=((2018-2014)/(2014-1999))*100
a
```

3)
```{r}
sum(4,5,8,11)
```

4)
```{r}
plot(rnorm(100))
```

5)
```{r}
help(sqrt)
```

6)
```{r}
plot(rnorm(100))
```

7)
```{r}
P = seq(from=31, to=60, by=1)
Q= matrix(P,ncol = 5, nrow = 6)
P
```
```{r}
Q
```
8)
```{r}
x1=seq(from=1, to=100, by=1)
x2=seq(from=101, to=200, by=1)
x3=seq(from=201, to=300, by=1)
t= data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```

9)
```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))
```

10)
```{r}
sqrt(mean(rnorm(100)))
```

11)
```{r}
d = data.frame(g = c(3,4,5),h = c(12,43,54))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt",header=TRUE)
d2$g*5
```

12)
```{r}
date1=strptime( c("20160127","20161003"),format="%Y%m%d")
present=c(10,6)
date1
```
```{r}
present
```
13)
```{r}
vector=seq(from=1, to=100, by=1)
s=c()
for(i in 1:100)
{
  if(vector[i]<5)
  {
    s[i]=vector[i]*5;
  }
  else if(vector[i]>90)
  {
    s[i]=vector[i]*10;
  }
  else
  {
    s[i]=vector[i]*0.1;
  }
}
s
```

14)
```{r}
fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
}
```


##Refrences##
1. https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
2. http://rmarkdown.rstudio.com/
  3. http://nicercode.github.io/guides/reports/
  4. http://kbroman.org/knitr_knutshell/pages/markdown.html
5. http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
6. https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
7. https://github.com/
  
  [^1]: https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
[^2]:http://rmarkdown.rstudio.com/
  [^3]:http://nicercode.github.io/guides/reports/
  [^4]:http://kbroman.org/knitr_knutshell/pages/markdown.html
[^5]:http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
[^6]:https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
[^7]:https://github.com/